A Formal Model of Checked C

### 2022-12-30 sandp23/overview.tex
add comments
update.

\section{Overview}
\label{sec:overview}

@@

We use the example of a simple network server in~\lst{lst:comb} to explain the overview of developers using~\systemname{}.
The~\lst{lst:comb} shows the C code of the redacted version of a simple network server with~\code{server_loop} as its entry point (\entrypoint).
The server runs in a loop and calls~\code{handle_request}, which handles each network request.
The function~\code{handle_request} reads data from the socket through~\code{read_msg} and based on the first byte, either~\code{process_req1} or~\code{process_req2} will be called to handle the request.

@@

@@

>>>>

\section{\systemname Compiler Overview}
\label{sec:overview}

@@

\Cref{fig:overview} provides the compiler structure of \systemname. The \systemname type checker compiles a \systemname program by partitioning the different program regions, i.e., $c$ and $uc$ regions, as well as different pointers, i.e., checked, unchecked and tainted pointers. Any $uc$ region pointers are executed within a sandbox, while checked pointers are executed via the \checkedc compiler.

\Cref{sec:formal} provides the formalism of the different compiler components.
Here,
we use the example of a simple network server in~\lst{lst:comb} to explain the \systemname compiler.
The~\lst{lst:comb} shows the C code of the redacted version of a simple network server with~\code{server_loop} as its entry point (\entrypoint).
The server runs in a loop and calls~\code{handle_request}, which handles each network request.
The function~\code{handle_request} reads data from the socket through~\code{read_msg} and based on the first byte, either~\code{process_req1} or~\code{process_req2} will be called to handle the request.

@@

\liyi{The example looks good. But we are focusing on converting C to \checkedc here? }

@@

\liyi{Can we just assume that programmers know \checkedc and will use \checkedc, and then we added tainted type? }
